---
title: "Coursework - Data Science I"
author: "Omar Zhadykov, 220220503"
output:
  html_notebook:
    fig_width: 10
    theme: spacelab
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document: default
  html_document:
    fig_width: 10
    theme: spacelab
    toc: yes
    toc_depth: 3
    toc_float: yes
---

<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
  });

});
</script>

```{r setup, warning=FALSE, message=FALSE, echo=FALSE}
library(svglite)
library(knitr)
suppressPackageStartupMessages(library(data.table))
library(ggplot2)
knitr::opts_chunk$set(dev = "svglite")

# Put your dataset in the same folder as your R file. This code will set your working directory for this notebook to the folder where the R file is stored. This way I can rerun your code without modifications.

library(rstudioapi)
setwd(dirname(getActiveDocumentContext()$path))
```

# Introduction

This coursework focuses on housing prices, with the main objective being to predict the price of a property based on various inputs. The inputs include features such as the area, the number and types of rooms, and additional factors like the availability of a main road, hot water heating, and more.

The dependent variable is the price, as it is the primary concern for most people searching for a house. The goal of this work is to predict the price based on diverse inputs, which consist of mixed data types, such as:

  - Numerical values
  - Text-based responses like "yes" or "no"
  - Categories for furnishing status, including "furnished," "semi-furnished," or "non-furnished."

This project addresses a regression problem because the objective is to predict a numeric value—in this case, the price of the property.

# Collection / Preparation 

Now we are going to import our dataset into this project.

```{r}
dt_houses <- fread(file = "./Datasets/Regression_set.csv")
```

<br>
I would like to check, if i have some nullish data in my dataset. I think it is a good idea to go through all rows and colums and check, if there is a NA. I want to check it with built-in function in R *complete.cases(data_table)*. This function returns TRUE or FALSE if row contains a NA value.

```{r}
nas <- dt_houses[!complete.cases(dt_houses)]
nas
```

That looks great, now we can explore our dataset :)

# Exploration

Explore your data by means of select summary statistics and visualizations and present interesting findings to your reader. 

Before we will explore our data, I want to import all libraries, which we will probably use:

```{r}
library(data.table)
library(ggcorrplot)
library(ggExtra)
library(ggplot2)
library(ggridges)
library(ggsci)
library(ggthemes)
library(RColorBrewer)
library(svglite)
library(viridis)
library(scales)
```

I found some helpful functions in R, so we could have a look on our data. We will start with a structure, than we will get some statistic data and take a *head()* of the data

```{r}
str(dt_houses)
```
<br>
Statistic data:
```{r}
summary(dt_houses[, .(price, area, bedrooms, bathrooms, stories, parking)])
```

<br>
and this is a sample of our dataset:

```{r}
head(dt_houses)
```

I would like to start from density of a main values, which are from my domain knowledge are important in price of the properties

We will start with price density: 

```{r}
ggplot(data = dt_houses, aes(x = price)) + 
  geom_density(fill="#f1b147", color="#f1b147", alpha=0.25) + 
  labs(
    x = 'Price',
    y = 'Density'
  ) +
  geom_vline(xintercept = mean(dt_houses$price), linetype="dashed") + 
  scale_x_continuous(labels = label_number(scale = 1e-6, suffix = "M")) + 
  theme_minimal() + 
  theme(axis.line = element_line(color = "#000000"))
```

Also it would be greate to have a look at area density:

```{r}
ggplot(data = dt_houses, aes(x = area)) + 
  geom_density(fill="#f1b147", color="#f1b147", alpha=0.25) + 
  labs(
    x = 'Price',
    y = 'Density'
  ) +
  theme_minimal() + 
  theme(axis.line = element_line(color = "#000000"))
```


<br>
This is interesting, how does area affect price of the house. We will plot it with points, where price is on the y-axis and area on x-axis.

```{r}
ggplot() + 
  geom_point(data = dt_houses, aes(x = area, y = price)) +
  scale_y_continuous(labels = label_number(scale = 1e-6, suffix = "M")) + 
  theme_minimal() + 
  theme(axis.line = element_line(color = "#000000"))
```

This looks nice, but we do not have any knowledge about areas, because they are mostly "ids" and they do not necessary contain "area-value" inside.

But, now I have the simplest idea, how does amount of bedrooms correlates with the price.

```{r}
ggplot(data = dt_houses, aes(x = factor(bedrooms), y = price)) +
  geom_boxplot() + 
  theme_minimal() 
```

We can see, that on average, more bedrooms, means higher price, but I think there is not really strong relationship between this two variables.

Also it would be great to take a look at a bedrooms histrogram:

```{r}
ggplot(data = dt_houses, aes(x = bedrooms)) + 
  geom_histogram(fill="#2f9e44", color="#2f9e44", alpha=0.25) + 
  geom_vline(xintercept = mean(dt_houses$bedrooms), linetype="dashed") + 
  theme_minimal() + 
  theme(axis.line = element_line(color = "#000000"))
```
Also I want to show you the mean of the bedrooms:
```{r}
mean(dt_houses$bedrooms)
```


Here we can see, that the most of the properties tend to have 2, 3 or 4 rooms. 

Let's also have a look at density and mean value of a stories:

```{r}
ggplot(data = dt_houses, aes(x = stories)) + 
  geom_histogram(fill="#2f9e44", color="#2f9e44", alpha=0.25) + 
  geom_vline(xintercept = mean(dt_houses$bedrooms), linetype="dashed") + 
  theme_minimal() + 
  theme(axis.line = element_line(color = "#000000"))
```

```{r}
ggplot(data = dt_houses, aes(y = price, x = area)) + 
  geom_point() +
  facet_grid(.~furnishingstatus) +
  scale_y_continuous(labels = label_number(scale = 1e-6, suffix = "M")) +
  theme_minimal() + 
  theme(axis.line = element_line(color = "#000000"))
```


```{r}

```

# Models 1 & 2

Run two regression or classification models with a minimum of 5 (identical!) inputs and evaluate them in detail: Compare their performance on your data (appropriate performance metric, performance on specific regions of the input/output space) and identify potential problems/shortcomings. 

If you tune a model (e.g. threshold of a logistic regression) for some metric, use only the final tuned version in the comparison with the other model. 

# Feature Engineering

Engineer a minimum of two new features based on your data exploration or on theoretical considerations. Add these features to your models and reevaluate their performance on the same performance metrics as before.

***




